### 2023-02-08 dissertation/chapters/01-introduction.tex
🚧  (article): Review, Anna part 1 a

The performance and capabilities of \acp{ANN} is largely influenced by the learning process used. The learning process consists of multiple components. These include the type of underlying optimisation algorithm used, how the model parameters are initialised, the hyper-parameters used and the constraints of learning such as allowed search space and boundaries. Each of these elements influence how much a particular learning technique might focus on a particular solution (exploitation), in comparison to seeking out novel solutions (exploration) during training.

@@

Many different heuristics have been developed and used to train \acp{FFNN}~\cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}. Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses. Finding the best heuristic to train the \acs{FFNN} is required in order to yield optimal results. This process is often non-trivial and could be a time-consuming exercise.  Consider that selection of the best heuristic as applied to optimisation problems, such as training \acp{FFNN}, is problem specific~\cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.

@@

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based \acp{MH} in real-valued dynamic optimization. However, research on the application of \acp{HH} in the context of \acs{FFNN} training is scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.

>>>>

The performance and capabilities of \acp{ANN} is largely influenced by the learning process used. The learning process consists of multiple components. These include the type of underlying optimisation algorithm used, how the model parameters are initialised, the hyper-parameters used and the constraints of learning such as allowed search space and boundaries. Each of these elements influences how much a particular learning technique might focus on a particular solution (exploitation), in comparison to seeking out novel solutions (exploration) during training.

@@

Many different heuristics have been developed and used to train \acp{FFNN}~\cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}. Each of these heuristics has different search behaviours, characteristics, strengths and weaknesses. Finding the best heuristic to train the \acs{FFNN} is required in order to yield optimal results. This process is often non-trivial and could be a time-consuming exercise.  Consider that selection of the best heuristic as applied to optimisation problems, such as training \acp{FFNN}, is problem specific~\cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.

@@

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based \acp{MH} in real-valued dynamic optimisation. However, research on the application of \acp{HH} in the context of \acs{FFNN} training is scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.

### 2023-02-08 dissertation/chapters/04-hyper-heuristics.tex
🍱 (images): Recovered
🚧  (article): Review, Anna part 1 a

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based \acp{MH} in real-valued dynamic optimization. Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training. The following section provides a framework for \acs{HH} classification.

@@

\begin{figure}[htbp]
      \centering
      \includegraphics[width=\textwidth]{images/hh_classification.pdf}
      \caption{A classification of \acs{HH} approaches, according to two dimensions: (i) the source of feedback used during learning, and (ii) the nature of the heuristic search space.}
      \label{fig:heuristics:hh:classification}
\end{figure}

>>>>

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based \acp{MH} in real-valued dynamic optimisation. Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training. The following section provides a framework for \acs{HH} classification.

@@

\begin{figure}[htbp]
      \centering
      \includegraphics[width=0.85\textwidth]{images/hh_classification.pdf}
      \caption{A classification of \acs{HH} approaches, according to two dimensions: (i) the source of feedback used during learning, and (ii) the nature of the heuristic search space.}
      \label{fig:heuristics:hh:classification}
\end{figure}

### 2023-02-08 dissertation/chapters/06-bayesian-hyper-heuristic.tex
Symbols done
🚧  (article): Review, Anna part 1 a

Generally speaking, the \index{heuristic pool}heuristic pool is a collection of low-level heuristics under consideration by the \acs{BHH}. The \index{heuristic pool}heuristic pool contains the set of low-level \index{heuristic}heuristics that, together with their performance information, make up the \text{heuristic space}. Importantly, the \acs{BHH} searches in \index{heuristic}heuristic space. The \index{heuristic pool}heuristic pool is defined in terms of the diversity of heuristics, as well as the number of heuristics in the \index{heuristic pool}heuristic pool. Each of these are discussed in the following sections.

@@

The \index{entity pool}entity pool maintains two different types of state. These include entity (local) and population (global) state. Each of these are discussed in more detail next.

@@

Entities represent candidate solutions to the model's trainable parameters (weights) and other \index{heuristic}heuristic-specific state parameters, as was discussed in Section \ref{sec:bhh:heuristic:proxies}. It can be said that entities implement \textit{local} state. It was mentioned that these entities can be treated as physical \textit{particles} in a hyper-dimensional search environment. Entities model concepts from physics. For example, the candidate solution is represented as the entity's position, and an entity's velocity and acceleration is analogous to the gradient and momentum of the entity respectfully. Examples of entity state parameters, as derived from various low-level \index{heuristic}heuristics, is given as follows:

@@

\begin{equation}
      \label{eq:bhh:selection_mechanism:numerical_stability:log_sum_exp}
      \begin{split}
            LSE(P(h_{k} \vert e_{j}, c_{1};  \theta, \phi, \psi)) = \ln(\exp(\phi_{j,k}) +  \exp(\psi_{k}) + \exp(\theta_{k}))
      \end{split}
\end{equation}

@@

\begin{itemize}
      \item using \textit{symmetric} initialisation of the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$;

@@

In probability theory and statistics, \acf{MLE} is a method that estimates the parameters of a prior probability distribution given newly observed data and evidence. This section shows that the values for $\boldsymbol{\theta}$, $\boldsymbol{\phi}$ and $\boldsymbol{\psi}$ can be estimated by \acs{MLE} as follows:

@@

      \item The low-level heuristics' hyper-parameters. At a lower-level, each of these heuristics have their own set of hyper-parameters.

>>>>

Generally speaking, the \index{heuristic pool}heuristic pool is a collection of low-level heuristics under consideration by the \acs{BHH}. The \index{heuristic pool}heuristic pool contains the set of low-level \index{heuristic}heuristics that, together with their performance information, make up the \text{heuristic space}. Importantly, the \acs{BHH} searches in \index{heuristic}heuristic space. The \index{heuristic pool}heuristic pool is defined in terms of the diversity of heuristics, as well as the number of heuristics in the \index{heuristic pool}heuristic pool. Each of these is discussed in the following sections.

@@

The \index{entity pool}entity pool maintains two different types of state. These include entity (local) and population (global) state. Each of these is discussed in more detail next.

@@

Entities represent candidate solutions to the model's trainable parameters (weights) and other \index{heuristic}heuristic-specific state parameters, as was discussed in Section \ref{sec:bhh:heuristic:proxies}. It can be said that entities implement \textit{local} state. It was mentioned that these entities can be treated as physical \textit{particles} in a hyper-dimensional search environment. Entities model concepts from physics. For example, the candidate solution is represented as the entity's position, and an entity's velocity and acceleration are analogous to the gradient and momentum of the entity respectfully. Examples of entity state parameters, as derived from various low-level \index{heuristic}heuristics, is given as follows:

@@

\begin{equation}
      \label{eq:bhh:selection_mechanism:numerical_stability:log_sum_exp}
      \begin{split}
            LSE(P(h_{k} \vert e_{j}, c_{1};  \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})) = \ln(\exp(\phi_{j,k}) +  \exp(\psi_{k}) + \exp(\theta_{k}))
      \end{split}
\end{equation}

@@

\begin{itemize}
      \item using \textit{symmetric} initialisation of the concentration parameters $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$;

@@

In probability theory and statistics, \acf{MLE} is a method that estimates the parameters of a prior probability distribution and is based on newly observed data and evidence. This section shows that the values for $\boldsymbol{\theta}$, $\boldsymbol{\phi}$ and $\boldsymbol{\psi}$ can be estimated by \acs{MLE} as follows:

@@

      \item The low-level heuristics' hyper-parameters. At a lower-level, each of these heuristics has their own set of hyper-parameters.

### 2023-02-08 dissertation/chapters/08-results.tex
🚧  (article): Review, Anna part 1 a

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichlet probability distribution}Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$. The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{\index{heuristic}heuristic selection probabilities}. Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively. Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool. Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
            \caption{$\alpha_{0}$ - \acs{SGD}}
            \label{fig:results:case_study:alphas:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
            \caption{$\alpha_{6}$ - \acs{Adam}}
            \label{fig:results:case_study:alphas:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
            \caption{$\alpha_{7}$ - \acs{PSO}}
            \label{fig:results:case_study:alphas:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
            \caption{$\alpha_{8}$ - \acs{GA}}
            \label{fig:results:case_study:alphas:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:alphas}
\end{figure}

@@

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
            \caption{P($\theta_{0} \vert \alpha_{0})$ - \acs{SGD}}
            \label{fig:results:case_study:thetas:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
            \caption{P($\theta_{6} \vert \alpha_{6})$ - \acs{Adam}}
            \label{fig:results:case_study:thetas:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
            \caption{P($\theta_{7} \vert \alpha_{7})$ - \acs{PSO}}
            \label{fig:results:case_study:thetas:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
            \caption{P($\theta_{8} \vert \alpha_{8})$ - \acs{GA}}
            \label{fig:results:case_study:thetas:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average sampled \index{heuristic}heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8. The \index{heuristic}heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:thetas}
\end{figure}

@@

Figures~\ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs. Similar to before, these illustrations are also presented in log scale.

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
            \caption{P($h_{0} \vert \theta_{0})$ - \acs{SGD}}
            \label{fig:results:case_study:p_H:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
            \caption{P($h_{6} \vert \theta_{6})$ - \acs{Adam}}
            \label{fig:results:case_study:p_H:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
            \caption{P($h_{7} \vert \theta_{7})$ - \acs{PSO}}
            \label{fig:results:case_study:p_H:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
            \caption{P($h_{8} \vert \theta_{8})$ - \acs{GA}}
            \label{fig:results:case_study:p_H:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average prior \index{heuristic}heuristic selection probabilities, $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8. The prior \index{heuristic}heuristic selection probabilities are sampled from the probability distribution of \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_H}
\end{figure}

>>>>

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichlet probability distribution}Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$. The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{\index{heuristic}heuristic selection probabilities}. Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, are at indices 0, 6, 7, and 8 respectively. Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool. Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
            \caption{$\alpha_{0}$ - \acs{SGD}}
            \label{fig:results:case_study:alphas:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
            \caption{$\alpha_{6}$ - \acs{Adam}}
            \label{fig:results:case_study:alphas:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
            \caption{$\alpha_{7}$ - \acs{PSO}}
            \label{fig:results:case_study:alphas:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
            \caption{$\alpha_{8}$ - \acs{GA}}
            \label{fig:results:case_study:alphas:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, are at indices 0, 6, 7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:alphas}
\end{figure}

@@

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
            \caption{P($\theta_{0} \vert \alpha_{0})$ - \acs{SGD}}
            \label{fig:results:case_study:thetas:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
            \caption{P($\theta_{6} \vert \alpha_{6})$ - \acs{Adam}}
            \label{fig:results:case_study:thetas:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
            \caption{P($\theta_{7} \vert \alpha_{7})$ - \acs{PSO}}
            \label{fig:results:case_study:thetas:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
            \caption{P($\theta_{8} \vert \alpha_{8})$ - \acs{GA}}
            \label{fig:results:case_study:thetas:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average sampled \index{heuristic}heuristic selection probabilities, denoted $\boldsymbol{\theta}$, are at indices 0, 6, 7, and 8. The \index{heuristic}heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:thetas}
\end{figure}

@@

Figures~\ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, are at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs. Similar to before, these illustrations are also presented in log scale.

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
            \caption{P($h_{0} \vert \theta_{0})$ - \acs{SGD}}
            \label{fig:results:case_study:p_H:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
            \caption{P($h_{6} \vert \theta_{6})$ - \acs{Adam}}
            \label{fig:results:case_study:p_H:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
            \caption{P($h_{7} \vert \theta_{7})$ - \acs{PSO}}
            \label{fig:results:case_study:p_H:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
            \caption{P($h_{8} \vert \theta_{8})$ - \acs{GA}}
            \label{fig:results:case_study:p_H:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average prior \index{heuristic}heuristic selection probabilities, $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, are at indices 0, 6, 7, and 8. The prior \index{heuristic}heuristic selection probabilities are sampled from the probability distribution of \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_H}
\end{figure}
